\documentclass{beamer}
\usetheme{Darmstadt}
\usecolortheme{default}
\usepackage{draftcopy}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{verbatim}
\beamertemplatenavigationsymbolsempty


\title{ECO364 (International Trade) Summer 2016}
\date{June 16, 2016}
\author[Scott Orr]{Scott Orr}
\institute{University of Toronto}

\AtBeginSection[]
{
	\begin{frame}
		\frametitle{Outline}
		\tableofcontents[currentsection]
	\end{frame}
}

\begin{document}
	
	\begin{frame}
		\titlepage
	\end{frame}
	
\begin{frame}
	\frametitle{Outstanding Issues}
\begin{itemize}
	\item Please hand in problem set 4
	\item Problem set answers will be posted today.
		\begin{itemize}
			\item Except problem set 4.
		\end{itemize}
	\item Final exam coverage.
		\begin{itemize}
			\item Everything covered in class/problem sets.
			\item Cumulative, but weighted more towards second half.
			\item 4 short answer (20\%), 2 medium answer (30\%), 2 long answer (50\%) 
		\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
	\frametitle{Outstanding Issues}
	\begin{itemize}
		\item Extra Office Hours:
		\begin{itemize}
			\item Leandro: Monday
				\begin{itemize}
					\item Time and location TBA on blackboard
				\end{itemize}
			\item Scott: Tuesday and Wednesday
				\begin{itemize}
				\item Tuesday: 11-12  GE 313
				\item Wednesday: 10-12 GE 313
				\end{itemize}
				\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Short Review of Second Half of Course}
Two Main Topics:
\begin{enumerate}
	\item Politics and Trade Policy
		\begin{itemize}
			\item Instruments of trade policy
				\begin{itemize}
					\item Tariffs, quotas, VERs, export subsidies.
				\end{itemize}
			\item Politics:
					\begin{itemize}
								\item Why implement trade barriers?
					\end{itemize}
			\end{itemize}
	\item Increasing Returns, Imperfect Competition, and Trade
		\begin{itemize}
			\item Monopoly
			\item Monopolistic Competition
			\item Monopolistic Competition with Heterogeneous firms
			\item External Economies of Scale
		\end{itemize}
\end{enumerate}

\end{frame}

\begin{frame}
	\frametitle{Trade Policy}

Trade policy and welfare
\begin{itemize}
	\item Tariffs, quotas, VERs and export subsidies hurt small open economies.
	\item Tariffs can benefit large open economies through a terms of trade effect.
\end{itemize}
Trade policy and politics
\begin{itemize}
	\item Why implement trade barriers?
		\begin{itemize}
			\item Distributional concerns, political incentives, collective action problems, terms of trade effects, infant industry effects. 
			\item Unilateral incentives to introduce tariffs due to a terms-of-trade effect problematic for world welfare
				\begin{itemize}
					\item Creates a role for trade institutions
				\end{itemize}
		\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Increasing Returns, Imperfect Competition, and Trade}
New gains from trade
	\begin{itemize}
		\item Gains from variety
		\item Pro-competitive gains
		\item Efficiency gains
			\begin{itemize}
				\item Due to increasing returns to scale
			\end{itemize} 
		\item Allocative gains from trade.
			\begin{itemize}
				\item Due to exit fo low-productivity firms and expanded output of high productivity firms.
			\end{itemize}
	\end{itemize}
Trade Inefficiencies?
	\begin{itemize}
		\item ``Technological Lock-in"
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Rest of Class:}
	
Practice Problems
\end{frame}

\end{document}